The Error Estimate of Force Calculation in the Heterogeneous Molecular Systems

### 2011-10-17 shortRange.inhomo/writeDown/main.tex
remove result of T=0.7, 1.1, 1.2

In a spacial heterogeneous system, the heterogeneity error may play a
dominate role in the simulation, (see examples in section
\ref{sec:tmp2}).  Since the mean error force can be calculated
by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
heterogeneity error is to correct the computed force by the mean error
force, namely
\begin{align}\label{eqn:define-fcorr}
  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
\end{align}
In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
is also refered as \emph{correction force} in the context of
long-range force correction. This correction works because it takes
into the force contribution outside the cut-off radius. The mean of
the corrected error force vanishes:
\begin{align}\label{eqn:mean-fcorr}
  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
   =
  \big\langle\,
  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
  \big\rangle = 0.
\end{align}
The mean square error is given by
\begin{align} \nonumber
  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
  & =
  \big\langle\,
  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E^2_{\textrm{homo}}(\v r) +
  \mathcal E^2_{\textrm{correlation}}(\v r),
\end{align}
containing no heterogeneity error.  It worth noticing that the mean
square error of the corrected force is nothing but the variance of the
uncorrected error force: $\langle\vert\Delta\v F_{\textrm{corr}}(\v
r)\vert^2\rangle = \textrm{Var}[\Delta\v F(\v r)]$, which contains no
heterogeneous contribution.

The idea of the long-range force correction is very similar to those
proposed by earlier works~\cite{guo1997long, mecke1997molecular,
  janecek2006long, shen2007comparative}. In these works, the density
profile is assumed varying on only one direction, and the system is
subdivided into slabs perpendicular to that direction to calculate the
energy/force correction. The advantange of the our force correction is
that it has no geometric restriction on the density profile of the
system, so can be used in a wider range of heterogeneous simulations.

@@

To extensively test the effectiveness of the proposed adaptive cut-off
and long-range force correction methods, we perform simulations at
$T^\ast = 0.70,\ 0.85,\ 1.10,\ 1.20$.  We test the liquid-vapor
equilibrium density and the surface tension defined by
\begin{align}
  \gamma = \frac12 \int_{L_x}
  \bigg[\,
  p_x(x) - \frac{p_y(x) + p_z(x)}{2}
  \,\bigg]
  \,\d dx.
\end{align}
Where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
pressure. The convergence of the properties of interest with respect
to the cut-off radius is considered.  For the adaptive cut-off
simulation, the ``cut-off radius'' means the largest cut-off radius
used in the simulation region.

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
  \caption{The convergence of the equilibrium gas and liquid density
    with respect to the cut-off radius. All densities are substracted
    by the reference value, namely, the liquid and vapor density
    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
    presents the results of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (LFC)
    method. }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
  \caption{The convergence of the surface tension with respect to the
    cut-off radius.  This figure presents the results of three
    methods, namely the uniform cut-off (URC), the adaptive cut-off
    (ARC) and the force correction (FC) method.  The results with and
    without heterogeneous pressure correction (HPC) are shown together
    for comparison. The reference surface tensions, shown by solid
    black lines, are measured by the uniform cut-off method with
    $r_c^\ast=13$ using HPC.}
  \label{fig:tmp6}
\end{figure}

In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
the equilibrium liquid/vapor densities and surface tension are
investigated with respect to increasing cut-off radius. The red, green
and blue points with error bars denote the results of uniform,
adaptive and long-range force correction, respectively.
In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
value measured by uniform cut-off simulations of $r_c^\ast = 13$.  The
gas densities are connected by the dashed lines, and the liquid
densities are connected by the solid lines to guide the eyes.  In
Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
points connected by the dashed lines) are presented with pressure
corrected surface tension (data points connected by solid lines) and
the reference surface tension measured by uniform cut-off simulations
at $r_c^\ast = 13$ with pressure correction.

@@

For all temperatures studied, the liquid and gas densities of the
uniform and the adaptive cut-off methods are almost identical at the
same cut-off radius. This observation is also true for the surface
tension, see Fig. \ref{fig:tmp6}. This indicates that controlling the
maximum of force error (see Tab. \ref{tab:tmp1}) and introducing
larger homogeneous force error in the bulk liquid/gas regions will not
disturb the accuracy of the equilibrium densities and surface tension.
The adaptive cut-off method roughly saves one half of the
computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
adaptive cut-off depends on the property of the system: if the bulk
regions dominate the system, and the density difference between the
bulk regions is big enough to produce large error in the interfacial regions,
then the adaptive cut-off will save a lot of
computational expense. On the other hand, if the interfacial region is
computationally intensive, the adaptive cut-off will not improve the efficency
greatly.

For the liquid/vapor densities, the long-range force correction method
presents a much better convergence than the uniform and adaptive
cut-off simulations. The properties perfectly converge when the cut-off
radius is equal to or larger than 5, and the convergence at a cut-off
as small as 3.5 is acceptable.  With the same cut-off radius, the
computational cost of the force correction is nearly the same as the
uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
time, the force accuracy is more than one order of maganitude better.
% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.

With the long-range pressure correction, the convergence of the
surface tension of all methods are greatly improved. The discrepancy
between the corrected and uncorrected pressure is the value of the
correction, which decreases with increasing cut-off radius. However,
even at $r_c^\ast=10$, the correction is not negligible for $T^\ast =
0.70$ and $T^\ast = 0.85$. At higher temperature, the statistical
uncertainty gets larger, and better convergence is achieved at smaller
cut-off radius.

Comparing the results of the force correction method at
$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the
force accuracy of the former method is 3--5 times worse than the later
(see Tab. \ref{tab:tmp1}), however, the
density and surface tension accuracies are comparable to and
sometimes even better than the later (see Fig. \ref{fig:tmp5} and
\ref{fig:tmp6}).
% In the force correction simulation, the
% heterogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the heterogeneity error.
Since the homogeneity error dominates in the former simulation and the
heterogeneity error dominates in the later, the above observation
indicates different errors play different roles in the simulations.
The homogeneity error is actually the variation of the corrected error
force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
implies that the corrected error force may point to any direction with
the same probability, and may be cancelled by itself in a long time
average.  The heterogeneity error, in contrast, stems from the
non-vanishing value of the mean error force, which is alway pointing
at one certain direction (the same direction as the low-to-high
density jump), and has no oppotunity to be self-cancelled.

>>>>

In a spacial heterogeneous system, the heterogeneity error may play a
dominate role in the simulation, (see examples in section
\ref{sec:tmp2}).  Since the mean error force can be calculated
by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
heterogeneity error is to correct the computed force by the mean error
force, namely
\begin{align}\label{eqn:define-fcorr}
  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
\end{align}
In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
is also refered as \emph{correction force} in the context of
long-range force correction. This correction works because it takes
into the force contribution outside the cut-off radius. The mean of
the corrected error force vanishes:
\begin{align}\label{eqn:mean-fcorr}
  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
   =
  \big\langle\,
  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
  \big\rangle = 0.
\end{align}
The mean square error is given by
\begin{align} \nonumber
  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
  & =
  \big\langle\,
  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E^2_{\textrm{homo}}(\v r) +
  \mathcal E^2_{\textrm{correlation}}(\v r),
\end{align}
containing no heterogeneity error.  It worth noticing that the mean
square error of the corrected force is nothing but the variance of the
corrected/uncorrected error force: $\langle\vert\Delta\v
F_{\textrm{corr}}(\v r)\vert^2\rangle = \textrm{Var}[\Delta\v
F_{\textrm{corr}}(\v r)] = \textrm{Var}[\Delta\v F(\v r)]$, which
contains no heterogeneous contribution.

The idea of the long-range force correction is very similar to those
proposed by earlier works~\cite{guo1997long, mecke1997molecular,
  janecek2006long, shen2007comparative}. In these works, the density
profile is assumed to be heterogeneous on only one direction, and the
system is subdivided into slabs perpendicular to that direction to
calculate the energy/force correction. The advantange of the our force
correction is that it has no geometric restriction on the density
profile of the system, so can be used in a wider range of
heterogeneous simulations.

@@

To test the effectiveness of the proposed adaptive cut-off and
long-range force correction methods, we measure the liquid-vapor
equilibrium density and the surface tension defined by
\begin{align}
  \gamma = \frac12 \int_{L_x}
  \bigg[\,
  p_x(x) - \frac{p_y(x) + p_z(x)}{2}
  \,\bigg]
  \,\d dx.
\end{align}
Where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
pressure. The convergence of the properties of interest with respect
to the cut-off radius is considered.  For the adaptive cut-off
simulation, the ``cut-off radius'' means the largest cut-off radius
used in the simulation region.

\begin{figure}
  \centering
  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.gas.eps} 
  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.liquid.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.gas.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.liquid.eps} 
  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.gas.eps} 
  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.liquid.eps} 
  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.gas.eps} 
  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.liquid.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.70.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.10.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.20.eps} 
  \caption{$T^\ast = 0.85$. The convergence of the equilibrium gas and
    liquid densities with respect to the cut-off radius. All densities
    are compared with the refence value (black solid line), namely,
    the liquid and vapor densities meansured with a uniform cut-off
    radius $r_c^\ast=13$. The gray region denotes the statistcal
    uncertainty of the reference value.  This figure presents the
    results of three methods, namely the uniform cut-off (URC), the
    adaptive cut-off (ARC) and the force correction (LFC) method. }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.85.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.10.eps} 
  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.20.eps} 
  \caption{$T^\ast = 0.85$. The convergence of the surface tension
    with respect to the cut-off radius.  This figure presents the
    results of three methods, namely the uniform cut-off (URC), the
    adaptive cut-off (ARC) and the long-range force correction (LFC)
    method.  The results with and without long-range pressure
    correction (LPC) are shown together for comparison. The reference
    surface tensions, shown by solid black lines, are measured by the
    uniform cut-off method with $r_c^\ast=13$ using LPC.}
  \label{fig:tmp6}
\end{figure}

\begin{table}
  \centering
  \caption{
    $T^\ast = 0.85$. The maximum RMS force error and computational cost of 
    three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the long-range
    force correction (LFC) method.
    The computational cost is the number of pairwise interaction 
    measurements, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|@{\extracolsep{\fill}}ccc}\hline\hline
    $r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
     &\textrm{URC} & $8.6\times 10^{-2}$ & 2.9 \\
 3.5 &\textrm{ARC} & $8.6\times 10^{-2}$ & 1.9 \\
     &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{1-4}
     &\textrm{URC} & $2.2\times 10^{-2}$ & 7.8 \\
 5.0 &\textrm{ARC} & $2.2\times 10^{-2}$ & 4.5 \\
     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{1-4}
     &\textrm{URC} & $4.5\times 10^{-3}$ & 24 \\
 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
     &\textrm{LFC} & $2.3\times 10^{-4}$ & 24 \\\cline{1-4}
     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
\end{table}

% \begin{table}
%   \centering
%   \caption{
%     The maximum RMS force error and computational cost of 
%     three methods, namely the uniform cut-off
%     (URC), the adaptive cut-off (ARC) and the long-range
%     force correction (LFC) method.
%     The computational cost is the number of pairwise interaction 
%     measurements, which should be mashine-independent.
%   }\label{tab:tmp1}
%   \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
%     $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
% %     & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
% %     &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
% %     & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
% %     &     &\textrm{LFC} & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
% %     &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
% % 0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
% %     &     &\textrm{LFC} & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
% %     &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
% %     &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
% %     &     &\textrm{LFC} & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
%     &     &\textrm{URC} & $8.6\times 10^{-2}$ & 2.9 \\
%     & 3.5 &\textrm{ARC} & $6.7\times 10^{-2}$ & 2.1 \\
%     &     &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
%     &     &\textrm{URC} & $2.2\times 10^{-2}$ & 7.8 \\
%     & 5.0 &\textrm{ARC} & $1.9\times 10^{-2}$ & 4.6 \\
%     &     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
%     &     &\textrm{URC} & $4.5\times 10^{-3}$ & 24 \\
% 0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
%     &     &\textrm{LFC} & $2.3\times 10^{-4}$ & 24 \\\cline{2-5}
%     &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
%     &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
%     &     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
%   \end{tabular*}
% %   \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
% %     $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
% %     & 3.5 &\textrm{LFC} & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
% %     &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
% %     & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
% %     &     &\textrm{LFC} & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
% %     &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
% % 1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
% %     &     &\textrm{LFC} & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
% %     &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
% %     &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
% %     &     &\textrm{LFC} & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
% % %     & 3.5 &\textrm{LFC} & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
% % %     &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
% % %     & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
% % %     &     &\textrm{LFC} & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
% % %     &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
% % % 1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
% % %     &     &\textrm{LFC} & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
% % %     &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
% % %     &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
% % %     &     &\textrm{LFC} & $3.3\times 10^{-5}$ & 31 \\\hline\hline
% %   \end{tabular*}
% \end{table}

In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
the equilibrium liquid/vapor densities and surface tension are
investigated with respect to the increasing cut-off radius. The red,
green and blue points with error bars denote the results of uniform,
adaptive cut-off methods and the long-range force correction,
respectively.  In Fig. \ref{fig:tmp5}, all densities are compared with
the reference value measured by the uniform cut-off simulation of
$r_c^\ast = 13$, with the statistcal uncertainty denoted by the gray
region. The densities are connected by the the solid lines to guide
the eyes.  In Fig. \ref{fig:tmp6}, the direct measures of surface
tension (data points connected by the dashed lines) are presented with
pressure corrected surface tension (data points connected by solid
lines).  The same as the reference densities, the reference surface
tension is measured by uniform cut-off simulations at $r_c^\ast = 13$
with long-range pressure correction.  Table \ref{tab:tmp1} presents
the maximum RMS force error and the computational expense of the the
mentioned methods at different cut-off radii. The computational cost
is given by the average number of pairwise interactions calculated by
the program, which is platform independent and serves as a good bench
mark.

@@

The liquid and gas densities of the uniform and the adaptive cut-off
methods are almost identical at the same cut-off radius, see
Fig. \ref{fig:tmp5}. This observation is also true for the surface
tension, see Fig. \ref{fig:tmp6}. This indicates that controlling the
maximum of force error (see Tab. \ref{tab:tmp1}) and introducing
larger homogeneous force error in the bulk liquid/gas regions will not
disturb the accuracy of the equilibrium densities and surface tension.
The adaptive cut-off method roughly saves 1/3 -- 1/2 of the
computational cost (see Tab. \ref{tab:tmp1}). The efficiency benefit
of the adaptive cut-off depends on the property of the system: if the
bulk regions dominate the system, and the heterogeneity produces large
interfacial force error, then the adaptive cut-off will save a lot of
computational expense. On the other hand, if the interfacial region is
computationally intensive, the adaptive cut-off will not improve the
efficency greatly.

The long-range force correction method presents a much better density
convergence than the uniform and adaptive cut-off simulations: the
equilibrium densities converge when the cut-off radius is only 3.5,
see Fig. \ref{fig:tmp5}. The maximum RMS force error is reduced by roughly
one order of maganitude, comparing to the uniform and adaptive cut-off
methods, see Tab. \ref{tab:tmp1}. The computationally cost of the
force correction method is the same as the uniform cut-off methods at
the same cut-off radius.

% With the
% same cut-off radius, the computational cost of the force correction is
% nearly the same as the uniform cut-off methods, see
% Tab. \ref{tab:tmp1}, and at the same time, the force accuracy is more
% than one order of maganitude better.

% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.
% We also observe that the liquid densities are systemetically higher
% than the reference results. This fact will be discussed later by
% comparing with literature results.

The surface tension result of the force correction without pressure
correction is only slightly better than the uniform and adaptive
cut-off methods without pressure correction, see Fig. \ref{fig:tmp6}.
With the long-range pressure correction, the convergence of the
surface tension of all methods are greatly improved.  The force
correction method converges at $r_c^\ast = 3.5$, and the
uniform/adaptive cut-off methods converge at $r_c^\ast = 7.5$.  The
discrepancy between the corrected and uncorrected tension is the
amount of the correction, which decreases with the increasing cut-off
radius. However, even at $r_c^\ast=10$, this correction is not
negligible.

Comparing the results of the force correction method at $r_c^\ast =
3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the force
accuracy of the former method is 3 times worse than the later (see
Tab. \ref{tab:tmp1}). The equilibrium density accuracy is better than
the later, and surface tension is as good as the later (see
Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
% In the force correction simulation, the
% heterogeneity error is screened out and the force error term is
% dominated by the homogeneity error. And in the uniform cut-off
% simulation the force error is dominated by the heterogeneity error.
Since the homogeneity error dominates in the former simulation and the
heterogeneity error dominates in the later, the above observation
indicates different natures of error play different roles in the
simulations.  The homogeneity error is actually the variation of the
corrected error force that has a vanished mean, see
Eqn. \eqref{eqn:mean-fcorr}. This implies that the corrected error
force may point to any direction with the same probability, and may be
cancelled by itself in a long time average.  The heterogeneity error,
in contrast, stems from the non-vanishing mean value of the error
force, which is alway pointing at one certain direction (the opposite
direction of the density gradient), and has low  oppotunity to be
self-cancelled.

% To verify our simulations, we compare our results in
% Tab. \ref{tab:comparison} with a wide range of results reported by
% literature~\cite{janecek2006long, lotfi1992vapour,
%   errington2003evaluating, ismail2007application}

% We list in Tab. \ref{tab:comparison} a wide range of results reported
% by literature~\cite{janecek2006long, lotfi1992vapour,
%   errington2003evaluating, ismail2007application}, as well as our
% uniform ($r_c^\ast = 13$) and force correction ($r_c^\ast = 5.0$)
% results for comparison. The abbreviations in the table are explained
% in the caption. The MC/LEC, MD/Ewald and our methods are direct
% simulation of the heterogeneous system. The MD/Npt+test particle and
% MC/GC-TMMC methods are simulation of homogeneous systems that do not
% have the difficulties of heterogeneity, and are believed to be more
% precise than direct simulations~\cite{shen2007comparative}.

% \begin{table}
%   \centering
%   \caption{Equilibrium densities and surface tension comparision 
%     with various literature results: Monte Carlo with long-range
%     energy correction (MC/LEC)~\cite{janecek2006long}, Npt+test
%     particle molecular dynamics (MD/Npt+test particle)~\cite{lotfi1992vapour},
%     grand-canonical transition-matrix Monte Carlo (MC/GC-TMMC)~\cite{errington2003evaluating},
%     molecular dynamics with dispersion term calculated by the Ewald
%     summation (MD/Ewald)~\cite{ismail2007application}
%     and uniform cut-off (URC) and long-range force correction (LFC) molecular dynamics
%     proposed by this work. The surface tensions of this work are
%     corrected by the long-range pressure correction.
%     The cut-off radius of the Ewald summation is for the real space.
%   }
%   \label{tab:comparison}
%   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}clllllc}\hline\hline
%   % \begin{tabular}{cccc|cccc}\hline\hline
%     $T^\ast$ & Method & $r_c^\ast$ & $\rho^\ast_{\textrm{liq}}$ & $\rho^\ast_{\textrm{vap}}$ & $\gamma^\ast$ & Source \\\hline
%     0.70 & MC/LEC               & 2.5      & 0.842(1)    & 0.0021(2)   & 1.21(2)   & \cite{janecek2006long}\\
%     0.70 & MD/Npt+test particle & 5.0      & 0.84266(18) & 0.00193(10) & -         & \cite{lotfi1992vapour}\\
%     0.70 & MC/GC-TMMC           & 1/2 box  & 0.8424(13)  & 0.001992(2) & 1.182(10) & \cite{errington2003evaluating}\\
%     % 0.70 & MD/Ewald             & 5.0(real)& 0.8414(1)   & 0.0020(0)   & 1.141(11) & \cite{ismail2007application}\\
%     0.70 & MD/URC               & 13.0     & 0.8423(2)   & 0.0020(0)   & 1.128(10) & this work \\
%     % 0.70 & MD/LFC               & 5.0      & 0.8424(2)   & 0.0021(1)   & 1.145(11) & this work \\\hline
%     0.70 & MD/LFC               & 3.5      & 0.8430(4)   & 0.00209(9)  & 1.139(16) & this work \\\hline
%     0.85 & MD/Npt+test particle & 5.0      & 0.77623(25) & 0.00970(22) & -         & \cite{lotfi1992vapour}\\
%     0.85 & MC/GC-TMMC           & 1/2 box  & 0.7760(10)  & 0.009611(9) & 0.837(2)  & \cite{errington2003evaluating}\\
%     % 0.85 & MD/Ewald             & 5.0(real)& 0.7750(1)   & 0.0098(0)   & 0.818(15) & \cite{ismail2007application}\\
%     0.85 & MD/URC               & 13.0     & 0.7758(3)   & 0.0098(1)   & 0.794(09) & this work \\
%     % 0.85 & MD/LFC               & 5.0      & 0.7760(4)   & 0.0098(1)   & 0.823(21) & this work\\\hline
%     0.85 & MD/LFC               & 3.5      & 0.7761(3)   & 0.00986(16) & 0.794(15) & this work\\\hline
%     1.10 & MC/LEC               & 2.5      & 0.642(1)    & 0.054(1)    & 0.33(2)   & \cite{janecek2006long}\\
%     1.10 & MD/Npt+test particle & 5.0      & 0.6401(12)  & 0.0533(14)  & -         & \cite{lotfi1992vapour}\\
%     1.10 & MC/GC-TMMC           & 1/2 box  & 0.6410(7)   & 0.05485(5)  & 0.343(2)  & \cite{errington2003evaluating}\\
%     % 1.10 & MD/Ewald             & 5.0(real)& 0.6383(1)   & 0.0553(0)   & 0.302(11) & \cite{ismail2007application}\\
%     1.10 & MD/URC               & 13.0     & 0.6399(9)   & 0.0560(8)   & 0.300(07) & this work\\
%     % 1.10 & MD/LFC               & 5.0      & 0.6405(9)   & 0.0553(6)   & 0.293(9)  & this work\\ \hline
%     1.10 & MD/LFC               & 3.5      & 0.6411(10)   & 0.0559(6)   & 0.302(11)  & this work\\ \hline
%     1.20 & MC/LEC               & 2.5      & 0.566(1)    & 0.109(2)    & 0.16(2)   & \cite{janecek2006long}\\
%     1.20 & MD/Npt+test particle & 5.0      & 0.5661(22)  & 0.0987(16)  & -         & \cite{lotfi1992vapour}\\
%     % 1.20 & MD/Ewald             & 5.0(real)& 0.5627(2)   & 0.0942(0)   & 0.156(14) & \cite{ismail2007application}\\
%     1.20 & MD/URC               & 13.0     & 0.5624(11)  & 0.1002(5)   & 0.131(6) & this work\\
%     % 1.20 & MD/LFC               & 5.0      & 0.5651(22)  & 0.0987(11)  & 0.136(17) & this work\\
%     1.20 & MD/LFC               & 3.5      & 0.5632(14)  & 0.1002(19)  & 0.130(8) & this work\\
%     \hline\hline
%   % \end{tabular}
%   \end{tabular*}
% \end{table}
